Project setup

### 2021-10-05 analysis/setup.Rmd
copy PHESANT and UKBB file directories to project directory in case they change with time

options("workflowr.view" = FALSE) # if using cluster
options("workflowr.view" = TRUE) # defaule, if using Rstudio on personal computer

@@

- Because Terminal cannot generate a preview and `workflowr` doesn't like the sysgit, to the `.Rprofile` file, add:
  - `options(workflowr.sysgit = "")`
  - `options("workflowr.view" = FALSE)`
- To ensure git hub isn't managing large files, modify the `.gitignore` file, by adding the following lines:
```
analysis/*
data/*
!analysis/*.Rmd
_targets
*.out
*.rds
*.RData
```
- Save and push these changes to GitHub.
- Pull to the server.

@@

Only do this once. The `Neale_SGG_directory.csv` file gives a summary of all SGG UKBB phenotypes that we have in our database and Neale phenotypes that have been downloaded. This file changes overtime as new phenotypes are requested from the UKBB and/or new Neale files are downloaded (i.e. more rows are added to the file). Because the `targets` package tracks input files and their changes, the current state of this file was copied to the project directory and this file was then used as an input file into the pipeline. This file is merely a reference file and changes to it don't correspond to changes in the underlying data used in the analyses.

```{r eval = FALSE}
Neale_summary_dir <- "/data/sgg2/jenny/data/Neale_UKBB_GWAS"
Neale_SGG_dir_org <- paste0(Neale_summary_dir,"/Neale_SGG_directory.csv") 
Neale_SGG_dir_cp <- paste0("data/Neale_SGG_directory_", format(Sys.Date(), "%d_%m_%Y"), ".csv")
file.copy(Neale_SGG_dir_org, Neale_SGG_dir_cp)
```

>>>>

options("workflowr.view" = FALSE) # if using cluster
options("workflowr.view" = TRUE) # default, if using Rstudio on personal computer

@@

- Because Terminal cannot generate a preview and `workflowr` doesn't like the sysgit, to the `.Rprofile` file, add:

```{r, engine = 'bash', eval = FALSE}
library("targets")

if(Sys.info()["sysname"]=="Linux"){
  options("workflowr.view" = FALSE)
}
```

- To ensure git hub isn't managing large files, modify the `.gitignore` file, by adding the following lines:
```
analysis/*
data/*
!analysis/*.Rmd
_targets
*.out
*.rds
*.RData
```
- Save and push these changes to GitHub.
- Pull to the server.

@@

Only do this once. The `Neale_SGG_directory.csv` file gives a summary of all SGG UKBB phenotypes that we have in our database and Neale phenotypes that have been downloaded. This file changes overtime as new phenotypes are requested from the UKBB and/or new Neale files are downloaded (i.e. more rows are added to the file). Because the `targets` package tracks input files and their changes, the current state of this file was copied to the project directory and this file was then used as an input file into the pipeline. This file is merely a reference file and changes to it doesn't correspond to changes in the underlying data used in the analyses.

Similarly, `PHESANT_file_directory.txt` and `UKBB_pheno_directory.csv` were copied once to the project directory in case more phenotypes were added to the SGG UKBB database and changed these files, but do not necessarily need to be added to the proxyMR project.

```{r eval = FALSE}
Neale_summary_dir <- "/data/sgg2/jenny/data/Neale_UKBB_GWAS"
UKBB_processed_dir <- "/data/sgg2/jenny/data/UKBB_processed"

Neale_SGG_dir_org <- paste0(Neale_summary_dir,"/Neale_SGG_directory.csv") 
PHESANT_dir_org <- paste0(UKBB_processed_dir,"/PHESANT/","PHESANT_file_directory.txt")
UKBB_dir_org <- paste0(UKBB_processed_dir,"/UKBB_pheno_directory.csv")

Neale_SGG_dir_cp <- paste0("data/Neale_SGG_directory_", format(Sys.Date(), "%d_%m_%Y"), ".csv")
PHESANT_dir_cp <- paste0("data/PHESANT_file_directory_", format(Sys.Date(), "%d_%m_%Y"), ".txt")
UKBB_dir_cp <- paste0("data/UKBB_pheno_directory_", format(Sys.Date(), "%d_%m_%Y"), ".csv")

file.copy(Neale_SGG_dir_org, Neale_SGG_dir_cp)
file.copy(PHESANT_dir_org, PHESANT_dir_cp)
file.copy(UKBB_dir_org, UKBB_dir_cp)
